GSEA datasets for FDR benchmarking

### 2017-12-09 datasets/GSEA/gsea.Rmd
Added code to plot boxplot of covariates for the overlaps between methods

any( is.na(genes) )
stopifnot(!any(is.na(genes)))
pwf <- nullp(genes, bias.data=geneLength )
goRes <- goseq( pwf, gene2cat=goSets )

@@

dplyr:::filter( goRes, numDEInCat > 0, numInCat > 15 ) %>%
  strat_hist( pval="over_represented_pvalue", covariate="numInCat", maxy=7)

@@

```{r plottingResults}
rejections_scatter( sGSEA, as_fraction=FALSE, supplementary=FALSE)

sGSEA <- estimatePerformanceMetrics(sGSEA, addColData=TRUE)

estimatePerformanceMetrics( sGSEA, alpha=0.1, tidy=TRUE ) %>%
  filter( blabel %in% c("lfdr","ihw-a10","bl-df03","qvalue","bh", "bonf") ) %>%
  select( blabel, value )

rejection_scatter_bins( sGSEA, "ind_covariate", threshold=15, bins=4, as_fraction=FALSE, supplementary=FALSE)
```

@@

getOverlapIndexes <- function( labs=c("lfdr", "ihw-a10"), alpha=0.1 ){
  rowSums( assays(sGSEA)[["qvalue"]][,labs] < alpha) == length(labs) &
  !(rowSums( assays(sGSEA)[["qvalue"]][,c("lfdr","ihw-a10","bl-df03","qvalue","bh", "bonf")] < alpha, na.rm=TRUE ) > (length(labs)))
}

set1 <- getOverlapIndexes( c("lfdr", "ihw-a10"), alpha=0.1 )
set2 <- getOverlapIndexes( c("lfdr","ihw-a10","bl-df03","qvalue","bh"), alpha=0.1 )
set3 <- getOverlapIndexes( c("lfdr","ihw-a10","bl-df03","qvalue","bh", "bonf"), alpha=0.1 )

sizesDf <- data.frame( 
  size=c( rowData( sGSEA )$ind_covariate[which(set1)], 
          rowData( sGSEA )$ind_covariate[which(set2)], 
          rowData( sGSEA )$ind_covariate[which(set3)] ),
  label=rep(c("set1", "set2", "set3"), c(sum(set1), sum(set2), sum(set3)) ) )

ggplot( sizesDf, aes( label, log2(size) )) +
  geom_boxplot()

dim(goRes)

goRes[set1,]

Plotting the methods overlap

sGSEASub <- sGSEA[,!apply( is.na( assays(sGSEA)[["qvalue"]] ), 2, all )]
sGSEASub <- sGSEASub[,-which(grepl("ihw", colData( sGSEASub )$blabel) & colData( sGSEASub )$param.alpha != 0.1)]
sGSEASub <- sGSEASub[,-which( grepl("bl", colData( sGSEASub)$blabel) & 
                   colData(sGSEASub)$param.smooth.df != 2L )]
sGSEASub <- sGSEASub[,!colData(sGSEASub)$blabel %in% "unadjusted"]

plotMethodsOverlap(sGSEASub, order.by = "freq", nsets=10)

@@

```{r, eval=FALSE }

nms <- names( genes )
xx <- seq_len(length(nms))
gns <- 1*( xx %in% sample( xx, 1000, replace=FALSE ) )
names( gns ) <- nms
pwf <- nullp( gns, bias.data=geneLength )
goRes <- goseq( pwf, gene2cat=goSets )
res <- goRes %>%
  dplyr:::filter( numDEInCat > 0 ) %>%
  dplyr:::select( c("over_represented_pvalue", "numInCat") ) %>%
  dplyr:::rename( pval = over_represented_pvalue, ind_covariate = numInCat )
pr <- designBen %>% buildBench( res, ftCols="ind_covariate")
assayNames(pr) <- "qvalue"
pr <- addDefaultMetrics(pr, metrics="rejections")

estimatePerformanceMetrics( pr, alpha=0.1, tidy=TRUE ) %>%
  filter( blabel %in% c("lfdr","ihw-a10","bl-df03","qvalue","bh", "bonf") ) %>%
  select( blabel, value )

>>>>

pwf <- nullp(genes, bias.data=geneLength )
goRes <- goseq( pwf, gene2cat=goSets )

@@

under_represented_pvalue
dplyr:::filter( goRes, numDEInCat > 0, numInCat > 10 ) %>%
  strat_hist( pval="over_represented_pvalue", covariate="numInCat", maxy=10)

@@

```{r plottingResults}
rejections_scatter( sGSEA, as_fraction=TRUE, supplementary=FALSE)

sGSEA <- estimatePerformanceMetrics(sGSEA, addColData=TRUE)
```

@@

methods <- c( "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf" )
plotCovariateBoxplots( sGSEA, alpha=0.1, nsets=6, methods=methods, trans=log2 )

@@

```{r, eval=FALSE }
nms <- names( genes )
xx <- seq_len(length(nms))
gns <- 1*( xx %in% sample( xx, 1000, replace=FALSE ) )
names( gns ) <- nms
pwf <- nullp( gns, bias.data=geneLength )
goRes <- goseq( pwf, gene2cat=goSets )
res <- goRes %>%
  dplyr:::filter( numDEInCat > 0 ) %>%
  dplyr:::select( c("over_represented_pvalue", "numInCat") ) %>%
  dplyr:::rename( pval = over_represented_pvalue, ind_covariate = numInCat )
pr <- designBen %>% buildBench( res, ftCols="ind_covariate")
assayNames(pr) <- "qvalue"
pr <- addDefaultMetrics(pr)
